	Once the pod group determines the design configuration of the pod, the
	dimensions are fed into the tube group. This group contains the sub-system
	analyses for the vacuum pumps, electromagnetic propulsion system, thermal
	management, and tube structure. Once the major aspects of the design of the
	tube are evaluated, results for both pod and tube design can be fed into
	mission and cost analyses to evaluate overall system performance
	requirements and their resulting costs.

\paragraph{Vacuum}
	The vacuum sub-system is a group that evaluates two phases of the vacuum
	use: pump down and steady-state usage. The pump down vacuum module
	evaluates the number of vacuum pumps and the energy required to pump the
	tube down from ambient pressure to the desired tube pressure.
	This information is critical because the vacuum will need to be pumped down
	once tube is constructed and in the event of an emergency pressurization.
	The vacuum pump down model is given in the equation
	\begin{equation}
		\label{eq:vacuum}
		E_{tot} = pwr * \frac{vol_{tube}*speed_{pump}*log(P_{0}/P_{f})*2}{t_{pumpdown}}* \gamma * 86400
	\end{equation}
	The pump down energy and weight of pumps will be critical for cost and structural analyses.
	The Vacuum group also considers the energy consumed during steady state operation.
	In theory, if the tube is perfectly air tight, there would be no need for
	the vacuum to run at all once the tube is pumped down. However, air is likely to be introduced
	to the system throughout normal operation, particularly during boarding. Consequently,
	vacuum pumps will need to used throughout operation to account for this.
	The effect of leakage rate on energy consumption is critical and will be
	discussed in more depth later. For the purpose of this analysis, the vacuum
	is modeled as a compressor using the same type of thermodynamic compressor
	model employed in the pod cycle analysis,
	with the same internal implicit solver.
	The pressure ratio of the vacuum will be equal to the ratio of ambient
	pressure to desired tube pressure and the mass flow through the vacuum at
	steady state will be equal to the leakage rate.
\paragraph{Thermal Management}
	A basic heat balance is performed to determine the approximate tube temperature.
	The quasi-steady analysis ignores heat transfer time lags and diurnal cycles.
	Heat is assumed to transfer and equilibrate rapidly between the pod compressor system,
	the rarified atmosphere inside the tube, the tube walls, and the outside environment.
	This is analysis is based off previous work by Chin\cite{Chin} and concludes
	manageable heat loads for air-cabin cooling. A conservative equilibrium
	tube temperature at full sun on a hot day and maximum pod operation is on
	the order of 110 degrees Farenheit.
	For an underground or underwater trajectory, these estimates would drop even lower.
\paragraph{Electromagnetic Propulsion}
	A series of linear synchronous motors (LSMs) is proposed to accelerate the
	pod from rest to top speed and maintain top speed with periodic boosts.
	While the specifications of the LSM system design are beyond the scope of
	this analysis, the amount of energy and power required of an LSM can be
	determined using the simple mechanics relationship
	\begin{equation}
		\label{eq:sum_of_forces}
		F_{net} = F_{LSM} + F_{thrust} - \frac{1}{2}C_{D}\rho V^{2}S - D_{mag}
	\end{equation}
	In which $F_{LSM}$ is the force required of the LSM system. This equation
	is integrated to determine the power and energy requirements for both
	startup and coasting booster sections. For the purpose of this analysis,
	the efficiency of the LSM is assumed to be .8 \cite{LSM}.
\paragraph{Structure}
	The structural analysis group determines the structural design of the tube
	for two phases of travel: travel over land and under water. When traveling
	overland, the tube is assumed to be supported by pylons above the terrain
	at a given height. For travel under water, the tube is assumed to be
	supported at a certain depth below sea level. The structural analysis in
	each phase is under constrained and allows for several free choices to be
	made by the user, which could have a significant impact on design
	configuration and material cost. To handle this challenge, the structural
	design of the tube at each phase will be optimized in order to determine
	the configuration that minimizes cost. The optimization methods will be
	discussed later in further detail.

