Using openMDAO and pyCycle2, a fully open-source model of the Hyperloop was
created to evaluate engineering and cost trade studies at the top level of the system.
The analyses presented illustrate the sensitivity of the overall system design
and performance to several key design variables.
First, it is shown that the coupling between tube pressure and the energy
consumption of different system components result in the existence of an
optimal tube pressure at which total energy consumption is minimal.
This optimal pressure and minimum energy consumption are shown to be coupled to
the tunnel leakage rate.
Second, this paper supports previous research that traveling at speeds above
Mach .8 is likely not practical as the tube size invariably becomes too large.
The coupling between tube size and boundary layer growth is analyzed to show
that the required size of the tube is very sensitive to boundary layer growth.
As a result, further research on the modeling and implementation active flow
control is recommended due to its potential to significantly reduce required tube size.
Finally, the system is shown to scale favorably with passenger pod capacity.
This allows each pod to carry more passengers than was previously proposed,
meaning the pod capacity can be optimized to meet market demand without
prohibitive costs to the operator. Although the model presented in this paper
is not of high fidelity, the trends and trade studies identified provide
valuable insight into the engineering behind the Hyperloop concept and how
these physical relationships can inform future design efforts. The open source,
modular nature of this system model will allow future researchers to modify,
adapt, and improve the model to include more specific subsystems
and higher fidelity modeling as needed.
The modeling platform is intended to serve as a publicly accessible baseline
that is easy to expand and delve deeper into this unique multidisciplinary system.